%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {BairesDev} % Organization
    {Arizona, US} % Location
    {Actual, Since April 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delegating tasks and achieving daily, weekly, and monthly goals..}
        \item {Built fully automated CI/CD pipelines on Jenkins/ArgoCD for containerized applications using Docker, AWS ECR and K8s.}
        \item {Restful micro services and architecture.}
        \item {Implemented several API micro services in .NET and in the Azure service bus and functions.}
        \item {Do code reviews.}
        \item {Performed unit/integration tests.}
        \item {Implementing Azure/Aws services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior .net developer} % Job title
    {F1 Solutions} % Organization
    {Canberra, Australia} % Location
    {Feb. 2021 - March. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching mid-level teammates.}
        \item {Upgrade system libraries bootstrap (from version 3 thru version 5), DevExpress, JQuery, JQuery UI and Ajax.}
        \item {Built and deployed overall service utilizing IIS, .NET and several Azure stack(Including Blob storage, service bus, functions, queues, webapps, aks, redis, artifactory), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Analyze and develop solutions for the product and act in the correction of defects.}
        \item {System development on WebAPI, ASP NET MVC, javascript, typescript.}
        \item {Used DevExpress Controls for rich data visualization while developing applications.}
        \item { Developed front-end application using JavaScript and AJAX to retrieve data and calling web services for updating the partial page without reloading the complete page.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior .net developer} % Job title
    {Squadra Technology} % Organization
    {Minas Gerais, Brazil} % Location
    {Feb. 2020 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Followed Agile methodologies (Scrum) and Test Driven Development, Pair Programming.}
        \item {Deployed the applications into the Azure and extracting the data from the Azure cloud services.}
        \item { Wrote SQL Queries,Stored procedures, Joins, Triggers to process large collection of products and used Data Reader, Data Adapter, SQL Command and Dataset for retrieving data from database using MS SQL.}
          \item {Used ADO.NET extensively to access the database.}
          \item {Implemented server caching techniques, state management, windows and Forms Authentication in ASP.NET.}
          \item {Participated in Requirement Analysis study and Involved in requirements gathering.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.Net developer} % Job title
    {Reply} % Organization
    {Minas Gerais, Brazil} % Location
    {Apr. 2018 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Ensure appropriate knowledge transfer to enable technology teams to design and implement
appropriate safeguards.}
        \item {Provide a remediation solution and follow up until it takes place.}
        \item {Followed Agile methodology with daily scrum meetings and providing user story updates. Worked with JIRA as an ALM tool for the central view for user stories and the bug tracking.}
        \item {Developed various stored procedures for the data retrieval from the database and generating different reports using SQL reporting services (SSRS).}
        \item {Used C\#, MVC, ASP.Net Web API , web forms in the application with MVC 5.0 Razor Engine. Service layer was developed using ASP.Net Web API for RESTful services.}
        \item {Used the NUnit/xUnit for unit testing of the classes.}
        \item {Maintaining and setting up new IIS application pools across multiple domains.}
        \item {Implemented OO Design and Concepts data modeling to analyze and define data requirements need to support business.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {system analyst and developer} % Job title
    {SIAT Informatica LTDA} % Organization
    {Minas Gerais, Brazil} % Location
    {Jan. 2015, - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided business analysis support and technical support and guidance to customers.}
        \item {Developing of desktop app for a shipping company (C\#, WPF, XAML, MVVM, MS SQL)..}
        \item {Mentors other software developers}
        \item {Follow architectural guidelines and code standards within the company.}
        \item {Prepare technical design documents based on business requirements.}
        \item {Designed an SOAP messages used in WCF to transfer information. Created Interfaces in C\# to communicate through the WCF services.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
